\vspace{\baselineskip} The population of long-period transiting exoplanets \vspace{-2.5\baselineskip}

### 2016-07-27 document/ms.tex
minor edit & GAIA may help with EB FAP

A study of the population of long-period transiting planets complements other
planet detection techniques, such as radial velocity \citep[for
example][]{Cumming:2008, Knutson:2014, Bryan:2016}, microlensing \citep[for
example][]{Gould:2010, Cassan:2012, Clanton:2014, Shvartzvald:2016}, and
direct imaging \citep[for example][]{Bowler:2016}.
The marriage of the radial velocity and transit techniques is particularly
powerful as exoplanets with both mass and radius measurements can be used to
study planetary compositions and the formation of planetary systems \citep[for
example][]{Weiss:2014, Rogers:2015, Wolfgang:2016}.
Unfortunately the existing catalog of exoplanets with measured densities is sparsely
populated at long orbital periods;  this makes discoveries with the transit method
at long orbital period compelling targets for follow-up observations.
Furthermore, even at long orbital periods, the \kepler\ light curves should be
sensitive to planets at the detection limits of the current state-of-the-art
radial velocity surveys.

There are two main technical barriers to a systematic search for single
transit events.
The first is that the transit probability for long-period planets is very low;
scaling as $\propto P^{-5/3}$ for orbital periods $P$ longer than the
baseline of contiguous observations.
Therefore, even if long-period planets are intrinsically common, they will
be underrepresented in a transiting sample.
The second challenge is that there are many signals in the observed light
curves caused by stochastic processes~--~both instrumental and
astrophysical~--~that can masquerade as transits.
Even when the most sophisticated methods for removing this variability are
used, false signals far outnumber the true transit events in any traditional
search.

@@

In detail, at each proposal time $t_0$, we hypothesize a box-shaped transit
with duration $\tau$
\begin{eqnarray}
m(t) &=& \left\{\begin{array}{ll}
    \mu - \delta, & \mbox{\,if $|t - t_0| < \tau/2$} \\
    \mu, & \mbox{\,otherwise}
\end{array}\right. \quad.
\end{eqnarray}
Assuming that the uncertainties on the observed fluxes $f(t)$ are Gaussian
with known variance ${\sigma_f}^2$, the likelihood function for the mean flux
$\mu$ and transit depth $\delta$ can be analytically computed to be a
two-dimensional Gaussian with mean and covariance given by linear
least-squares.
This likelihood function provides a natural scalar objective: the
signal-to-noise of the measured depth computed as a function of time.
In principle this scalar is also a function of duration but we only use a
single transit duration because the following steps in this procedure are only
sensitive to transits with very high signal-to-noise, and in practice, the
final results are insensitive to the specific choice of duration.

@@

In this step of the method, the goal is to discard any signals that are not
sufficiently ``transit-like'' in shape.
This step is similar to the method independently developed and recently
published by the \kepler\ team \citep{Mullally:2016}.
To quantify the quality of a candidate, we perform a model comparison between
a physical transit model and a set of other parameterized models for
systematics.
In order for a candidate to pass this vetting step, the transit model must be
``preferred'' to any other model as measured using the Bayesian Information
Criterion (BIC).
The BIC is not the optimal choice for this model comparison, but it is more
computationally tractable than the alternatives, such as computing thousands
of precise marginalized likelihoods or expected utilities for each model.
The BIC can be efficiently computed and it exhibits the desired
behavior~--~decreasing with increasing likelihood but flexible models are
penalized~--~and we find that it performs sufficiently well in practice.

@@

Since the search procedure described here was tuned to discover transit
signals, we do not consider the distribution or potential astrophysical nature
of any models besides the \modelname{transit} model.
In the future, it would be interesting to relax this goal and investigate the
other model classes; in particular, the \modelname{box} model is
sensitive to astrophysical phenomena, notably occultations of white dwarfs.
In a cursory investigation it is clear that the majority of signals labeled
\modelname{box} in our analysis are noise; however, a subset are likely to be
astrophysical in nature.

@@

For each transit candidate, we constrain the physical parameters of the system
by fitting a section of light curve around each transit using an exposure-time
integrated  Keplerian orbit with a quadratic limb darkening law for the
central body\footnote{\url{https://github.com/dfm/transit}; in this work, we
use git commit \textsf{482d99b}.}.
It has previously been established that the orbital period of a transiting
planet with only one transit can still be constrained given a measurement of
the stellar density and an assumption about the orbital eccentricity \cite[for
example][]{Wang:2015, Osborn:2016}.
Qualitatively this works because the transit of a bound body cannot have an
arbitrary period for a given duration.
This is the same argument used to justify the ``photoeccentric effect''
\citep{Dawson:2012} and the method of ``asterodensity profiling''
\citep{Kipping:2014b}.
In particular, this suggests that the periods of single transits in systems
with multiple inner planets will be especially well constrained
\citep{Kipping:2012}.
In this \paper, we do not take advantage of the extra constraints provided by
the inner planets, instead treating each long-period transiting system in
isolation, but this would be a good follow-up project.

@@

The candidate in the light curve of KIC~4754460 is an individual transit
candidate but another deeper eclipse can be found at a \kepler\ Barycentric
Julian Date (KBJD) of 1587.13; right at the beginning of Quarter 17.
This eclipse was missed by the automated search because only the second half
of the eclipse is observed.
The most likely explanation of this system is that the listed candidate is the
secondary eclipse of a binary system but we will keep the candidate in the
list and treat this effect statistically in \sect{false-positives}.

@@

@@

\begin{figure*}~\\
\begin{center}
\includegraphics{figures/full_sample_plus_cands.pdf}
\end{center}
\caption{%
The catalog of long-period transiting exoplanet candidates (green points with
error bars) compared to the \kepler\ candidates (blue points) and confirmed
planets \citep[black points;][]{Morton:2016} found in our target sample, and
the Solar System (orange squares).
The thin black error bars to the left of each candidate indicate the minimum
period allowed for each candidate by the prior assumption that no other
transit occurred during the baseline of \kepler\ observations of the target.
The vertical solid line shows the absolute maximum period accessible to
transit searches that require at least three transits in the \kepler\ data.
\dfmfiglabel{full-sample}}~\\
\end{figure*}

@@

To measure the completeness of search procedure described in \sect{search}, we
exploit the fact that transit signals are sparse and rare.
Therefore, most light curves contain no transits and we can reliably measure
the recovery rate of our method on synthetic transit signals~--~with known
properties~--~injected into real light curves.
This procedure is standard practice in the transit literature and it has been
used to determine the completeness of the KOI catalog
\citep{Christiansen:2013, Christiansen:2015} and other independent transit
searches \citep{Petigura:2013, Dressing:2015, Foreman-Mackey:2015}.

@@

Using the catalog of exoplanet discoveries (\sect{catalog}) and the
measurement of the search completeness (\sect{completeness}), we can now
estimate the occurrence rate of long-period exoplanets.
To simplify the analysis, we will make the strong assumption that none of the
candidates are astrophysical false positives (the eclipse or occultation
of a stellar mass companion, around either the target star or a
faint background star).
We revisit this assumption and discuss its validity in the following section.
As a further simplification, we also neglect the measurement uncertainties on
the planet parameters (including orbital period).
This assumption is justified because we are only making high-level
measurements of the mean occurrence rate in bins larger than the
uncertainties.

@@

To determine to what extent the catalog of detections presented in this work
may contain such false positives, we simulate populations of detected signals
to predict how many we should expect.  To accomplish this, we use the Python
package
\exosyspop\footnote{\url{https://github.com/timothydmorton/exosyspop}; in this
work, we use git commit \textsf{e4f54288}.}, which
we developed for this purpose and utilizes the \project{isochrones}
package \citep{Morton:2015} for simulations of stellar populations.

@@

\begin{floattable}
\begin{deluxetable}{ccccccccc}
\tabletypesize{\scriptsize}
\caption{The predicted masses and radial velocity semi-amplitudes for the
candidates from Table~\ref{tab:catalog} \label{tab:masses}}
\include{masstab}
\tablecomments{The masses and radial velocity amplitudes are estimated based
on the measured radius using a probabilistic mass--radius relation
\citep{Chen:2016}.}
\end{deluxetable}
\end{floattable}

@@

A real concern about the detection of exoplanets from a single transit is that
follow-up and confirmation is difficult.
Since the period of the orbit is poorly constrained and transits are sparse,
any prediction of a subsequent transit time will be too uncertain to schedule
targeted photometric follow-up.
Instead, follow-up using radial velocity and astrometry are more promising.
For both radial velocity and astrometry, there is information about the
orbiting planets in measurements made at all times~--~not just during transit.
This allows observations to be scheduled without a well constrained orbital
period.
Furthermore, follow-up of any of these candidates using radial velocity or
astrometry would provide a measurement of the density of a planet that would
be valuable for the study of planetary compositions.

@@

In principle the \gaia\ Mission will be very sensitive to the astrometric
wobble produced by a long-period exoplanet \citep{Perryman:2014}.
To leading order, the astrometric signal strength is proportional to the
semi-major axis of the stellar (primary) reflex motion in angular units.
That is, detectability is related to the angle $\alpha$ given by
\begin{eqnarray}
\alpha &=& \frac{a}{D}\,\frac{M_{\mathrm p}}{M_{\mathrm s}} \quad ,
\end{eqnarray}
where $a$ is the semi-major axis, $D$ is the distance from the observer to the
primary, and $M_{\mathrm{p}}/M_{\mathrm{s}}$ is the planet-to-star mass ratio.

The single-visit precision of \gaia\ will vary with magnitude but is expected
to be on the order of 40\,$\mu$as at these magnitudes.
In detail the confidence with which an exoplanet can be detected or measured
in the final \gaia\ data depends on this precision, the number of crossings of
the star through the \gaia\ field-of-view, and details of how the projected
orbit is sampled by the time history of the focal-plane crossings.
However, it is not expected that \gaia\ can detect or precisely measure
exoplanet-induced astrometric wobbles that are much smaller in amplitude than
the single-visit precision \citep{Perryman:2014}.

The primary stars in the \kepler\  Field are typically at distances of $\sim
500$\,pc, and typical mass ratios are in the $10^{-4}$ range.
We therefore expect astrometric amplitudes in the 0.3 to 3\,$\mu$as range.
These planets will not be detectable or measurable in the \gaia\ data under
any circumstances.
However, similar planets around closer stars \emph{will} be detectable with
\gaia.
This means that there will be a comparable exoplanet occurrence rate
measurement from the \gaia\ data.
It also means that many of the discoveries of the \KT\ and \tess\ missions
could be followed up and precisely measured by the \gaia\ Mission.

@@

We have developed a fully automated method to search for the transits of
long-period exoplanets with only one or two observable transits in the
\kepler\ archival light curves.
This method uses probabilistic model comparison to veto non-transit signals.
Applying this method to the brightest \numtargets\ G/K dwarfs in the \kepler\
target list, we discover \numcands\ systems with likely astrophysical
transits and eclipses.
We fit the light curve for each candidate with a physical generative model and
informative priors on eccentricity and stellar density to estimate the
planet's orbital period.
The constraint on the period is also informed by the simplifying assumption
that no other transit could occur during the baseline of \kepler\ observations
of the target.
Simulations of the false positive population~--~lone primary or secondary
eclipses of binary systems or background eclipsing binaries~--~suggest that 13
of these candidates have high probability of being planetary in nature.

@@

Using a probabilistic mass--radius relationship, we predict the masses of our
candidates and report predictions for the radial velocity amplitudes.
Unfortunately, since the target stars are faint and the amplitudes are small,
these targets are unlikely to be accessible with even the current
state-of-the-art high-precision instruments.
We also discuss the potential for astrometric follow-up using the forthcoming
data from the \gaia\ Mission with similarly discouraging results.

Any detailed analysis of individual systems detected with only a single
transit requires follow-up observations to convincingly rule out false
positive scenarios and to better characterize the stellar host parameters
(with, for example, parallax measurements from \gaia).
The conclusions of this work~--~and all other occurrence rate results based on
\kepler\ data~--~are conditioned on the assumption that the stellar
characterization of the target sample is systematic and un-biased.
The main population-level results should be fairly insensitive systematic
issues with the sample but a rigorous analysis of these effects will be
required to come to more detailed conclusions about this population of
long-period transiting planets.

@@

% \acknowledgments
\vspace{1.5em}
It is a pleasure to thank
Jeff Coughlin,
So Hattori,
Heather Knutson,
Hans-Walter Rix,
Dun Wang,
and
Angie Wolfgang
for helpful discussions and contributions.

>>>>

A study of the population of long-period transiting planets complements other
planet detection techniques, such as radial velocity \citep[for
example][]{Cumming:2008, Knutson:2014, Bryan:2016}, microlensing \citep[for
example][]{Gould:2010, Cassan:2012, Clanton:2014, Shvartzvald:2016}, and
direct imaging \citep[for example][]{Bowler:2016} surveys.
The marriage of the radial velocity and transit techniques is particularly
powerful as exoplanets with both mass and radius measurements can be used to
study planetary compositions and the formation of planetary systems \citep[for
example][]{Weiss:2014, Rogers:2015, Wolfgang:2016}.
Unfortunately the existing catalog of exoplanets with measured densities is sparsely
populated at long orbital periods;  this makes discoveries with the transit method
at long orbital period compelling targets for follow-up observations.
Furthermore, even at long orbital periods, the \kepler\ light curves should be
sensitive to planets at the detection limits of the current state-of-the-art
radial velocity surveys.

There are two main technical barriers to a systematic search for single
transit events.
The first is that the transit probability for long-period planets is very low;
scaling as $\propto P^{-5/3}$ for orbital periods longer than the
baseline of contiguous observations.
Therefore, even if long-period planets are intrinsically common, they will
be underrepresented in a transiting sample.
The second challenge is that there are many signals in the observed light
curves caused by stochastic processes~--~both instrumental and
astrophysical~--~that can masquerade as transits.
Even when the most sophisticated methods for removing this variability are
used, false signals far outnumber the true transit events in any traditional
search.

@@

In detail, at each proposal time $t_0$, we hypothesize a box-shaped transit
with duration $\tau$
\begin{eqnarray}
m(t) &=& \left\{\begin{array}{ll}
    \mu, & \mbox{\,if $|t - t_0| < \tau/2$} \\
    \mu - \delta, & \mbox{\,otherwise}
\end{array}\right. \quad.
\end{eqnarray}
Assuming that the uncertainties on the observed fluxes $f(t)$ are Gaussian
with known variance ${\sigma_f}^2$, the likelihood function for the mean flux
$\mu$ and transit depth $\delta$ can be analytically computed to be a
two-dimensional Gaussian with mean and covariance given by linear
least-squares.
This likelihood function provides a natural scalar objective: the
signal-to-noise of the measured depth computed as a function of time.
In principle this scalar is also a function of duration but we only use a
single transit duration because the following steps in this procedure are only
sensitive to transits with very high signal-to-noise, and in practice, the
final results are insensitive to the specific choice of duration.

@@

In this step of the method, the goal is to discard any signals that are not
sufficiently ``transit-like'' in shape.
This step is similar to the method independently developed and recently
published by the \kepler\ team \citep{Mullally:2016}.
To quantify the quality of a candidate, we perform a model comparison between
a physical transit model and a set of other parameterized models for
systematics.
In order for a candidate to pass this vetting step, the transit model must be
``preferred'' to any other model as measured using the Bayesian Information
Criterion (BIC).
The BIC is not the optimal choice for this model comparison, but it is more
computationally computationally tractable than the alternatives, such as
computing thousands of precise marginalized likelihoods or expected utilities
for each model.
The BIC can be efficiently computed and it exhibits the desired
behavior~--~decreasing with increasing likelihood but flexible models are
penalized~--~and we find that it performs sufficiently well in practice.

@@

Since the search procedure described here was tuned to discover transit
signals, we do not consider the distribution or potential astrophysical nature
of any models besides the \modelname{transit} model.
In the future, it would be interesting to relax this goal and investigate the
other model classes; in particular, the \modelname{box} model is
sensitive to astrophysical phenomena, notably occultations of white dwarfs,
which produce a perfect box-shaped signal.  In a cursory investigation
it is clear that the majority of signals labeled
\modelname{box} in our analysis are noise; however, a subset are likely to be
astrophysical in nature.

@@

For each transit candidate, we constrain the physical parameters of the system
by fitting a section of light curve around each transit using an exposure-time
integrated  Keplerian orbit with a quadratic limb darkening law for the
central body\footnote{Implemented at \url{https://github.com/dfm/transit};
this \paper\ uses git commit \textsf{482d99b} of that repository.}.
It has previously been established that the orbital period of a transiting
planet with only one transit can still be constrained given a measurement of
the stellar density and an assumption about the orbital eccentricity \cite[for
example][]{Wang:2015, Osborn:2016}.
Qualitatively this works because the transit of a bound body cannot have an
arbitrary period for a given duration.
This is the same argument used to justify the ``photoeccentric effect''
\citep{Dawson:2012} and the method of ``asterodensity profiling''
\citep{Kipping:2014b}.
In particular, this suggests that the periods of single transits in systems
with multiple inner planets will be especially well constrained
\citep{Kipping:2012}.
In this \paper, we do not take advantage of the extra constraints provided by
the inner planets, instead treating each long-period transiting system in
isolation, but this would be a good follow-up project.

@@

@@

The candidate in the light curve of KIC~4754460 is an individual transit
candidate but another deeper eclipse can be found at a KBJD of 1587.13; right
at the beginning of Quarter 17.
This eclipse was missed by the automated search because only the second half
of the eclipse is observed.
The most likely explanation of this system is that the listed candidate is the
secondary eclipse of a binary system but we will keep the candidate is the
list and treat this effect statistically in \sect{false-positives}.

In \dfmfig{obs-dist}, we compare the \emph{observed} period and radius
distributions of our discoveries to the longest-period planet candidates
discovered transiting stars in our target list by the official \kepler\
transit search \citep{Coughlin:2016}.
These histograms do not take uncertainties or detection efficiency into
account so any conclusions based on these plots should be taken with caution.
That being said, the apparent deficit of planets in the period range between
600 and 1000~days cannot be explained by selection effects~--~in fact, the
decreasing geometric transit probability and decreased orbital phase coverage at
longer periods exacerbates the signal~--~and should be
investigated more thoroughly.  The decline at longer periods can be attributed
to the declining transit detection probability.
We postulate three scenarios and expect that the observed effect is the result
of some combination of the three:
\begin{itemize}
{\item the periods of some candidates are overestimated and the missing second
transit occurs in a data gap,}
{\item overestimated stellar densities leading to an overestimate of the
orbital periods and an underestimate of the radii, or}
{\item a physical rise in the frequency of giant planets at long orbital
periods.}
\end{itemize}
The first two scenarios could be confirmed or ruled out by detailed analysis
of each candidate system and follow-up data.
Any result would be physically interesting but a rigorous analysis that is
beyond the scope of this \paper\ would be required to make a conclusive claim.

The difference between the observed radius distributions apparent in
\dfmfig{obs-dist} can be attributed to the drop off in sensitivity of our
search at small planet radius depicted in \dfmfig{completeness}.
The \kepler\ survey, on the other hand, has increasing sensitivity to smaller
planets due to the addition of multiple transits at shorter period.

@@

\begin{figure*}~\\
\begin{center}
\includegraphics{figures/full_sample_plus_cands.pdf}
\end{center}
\caption{%
The catalog of long-period transiting exoplanet candidates (green points with
error bars) compared to the \kepler\ candidates (blue points) and confirmed
planets \citep[black points;][]{Morton:2016}, and the Solar System (orange
squares).
The vertical dashed line indicates the full lifetime of the \kepler\ Mission;
planets with orbital periods longer than this will show at most one transit.
The vertical solid line shows the absolute maximum period accessible to
transit searches that require at least three transits.
\dfmfiglabel{full-sample}}~\\
\end{figure*}

@@

To measure the completeness of the search procedure described in \sect{search}, we
exploit the fact that transit signals are sparse and rare.
Therefore, most light curves contain no transits and we can reliably measure
the recovery rate of our method on synthetic transit signals~--~with known
properties~--~injected into real light curves.
This procedure is standard practice in the transit literature and it has been
used to determine the completeness of the KOI catalog
\citep{Christiansen:2013, Christiansen:2015} and other independent transit
searches \citep{Petigura:2013, Dressing:2015, Foreman-Mackey:2015}.

@@

Using the catalog of exoplanet discoveries (\sect{catalog}) and the
measurement of the search completeness (\sect{completeness}), we can now
estimate the occurrence rate of long-period exoplanets.
To simplify the analysis, we will make the strong assumption that none of the
candidates are astrophysical false positives (the eclipse or occultation
of a stellar mass companion, around either the target star or a
faint background star).
We revisit this assumption and discuss its validity in the following section.
As a further simplification, we also neglect the measurement uncertainties on
the planet parameters (including orbital period).
This assumption is only justified because we are only making high-level
measurements of the mean occurrence rate in bins larger than the uncertainties.

@@

To determine to what extent the catalog of detections presented in this work
may contain such false positives, we simulate populations of detected signals
to predict how many we should expect.  To accomplish this, we use the Python
package
\exosyspop\footnote{\url{https://github.com/timothydmorton/exosyspop}; in this
work we use commit \textsf{e4f54288}}, which
we developed for this purpose and utilizes the \project{isochrones}
package \citep{Morton:2015} for simulations of stellar populations.

@@

\begin{floattable}
\begin{deluxetable}{ccccccccc}
\tabletypesize{\scriptsize}
\caption{The predicted masses and radial velocity signals for the candidates
from Table~\ref{tab:catalog} \label{tab:masses}}
\include{masstab}
\tablecomments{The masses and radial velocity amplitudes are estimated based
on the measured radius using a probabilistic mass--radius relation
\citep{Chen:2016}.}
\end{deluxetable}
\end{floattable}

@@

A real concern about the detection of exoplanets from a single transit is that
follow-up and confirmation is difficult.
Since the period of the orbit is poorly constrained and transits are sparse,
any prediction of a subsequent transit time will be too uncertain to schedule
targeted photometric follow-up.
Instead, follow-up using radial velocity and astrometry are more promising.
For both radial velocity and astrometry, there is information about the
orbiting planets in measurements made at all times~--~not just during transit.
This allows observations to be scheduled without a well constrained orbital
period.
Furthermore, follow-up of any of these candidates using radial velocity or
astrometry would provide a measurement of the density of a planet that would
be invaluable for the study of planetary compositions.

@@

In priniciple the \gaia\ Mission will be very sensitive to the astrometric
wobble produced by a long-period exoplanet \citep{Perryman:2014}.
To leading order, the astrometric signal strength is proportional to the
semi-major axis of the stellar (primary) reflex motion in angular units.
That is, detectability is related to the angle $\alpha$ given by
\begin{eqnarray}
\alpha &=& \frac{a}{D}\,\frac{M_{\mathrm p}}{M_{\mathrm s}} \quad ,
\end{eqnarray}
% obviously fix to your notation!
where $a$ is the semi-major axis, $D$ is the distance from the observer to the
primary, and $M_{\mathrm{p}}/M_{\mathrm{s}}$ is the planet-to-star mass ratio.

The single-visit precision of \gaia\ will vary with magnitude but is expected
to be on the order of 40\,$\mu$as at these magnitudes.
In detail the confidence with which an exoplanet can be detected or measured
in the final \gaia\ data depends on this precision, the number of crossings of
the star through the \gaia\ focal plane, and details of how the projected
orbit is sampled by the time history of the focal-plane crossings.
However, it is not expected that \gaia\ can detect or precisely measure
exoplanet-induced astrometric wobbles that are much smaller in amplitude than
the single-visit precision \citep{Perryman:2014}.

The primary stars in the \kepler\  Field are typically at distances of $\sim
500$\,pc, and typical mass ratios are in the $10^{-4}$ range.
We therefore expect astrometric amplitudes in the 0.3 to 3\,$\mu$as range.
These planets will not be detectable or measurable in the \gaia\ data under
any circumstances, but it may be possible to identify which candidates are 
false-alarms caused by eclipsing binaries.
However, similar planets around closer stars \emph{will} be detectable with
\gaia.
This means that there will be a comparable exoplanet occurrence rate
measurement from the \gaia\ data.
It also means that many of the discoveries of the \KT\ and \tess\ missions
could be followed up and precisely measured by the \gaia\ Mission.

@@

We have developed a fully automated method to search for the transits of
long-period exoplanets with only one or two observable transits in the
\kepler\ archival light curves.
This method uses probabilistic model comparison to veto non-transit signals.
Applying this method to the brightest \numtargets\ G/K dwarfs in the \kepler\
target list, we discover \numcands\ systems with likely astrophysical
transits and eclipses.
We fit the light curve for each candidate with a physical generative model and
informative priors on eccentricity and stellar density to estimate the
planet's orbital period.
Simulations of the false positive population~--~lone primary or secondary eclipses of
binary systems or background eclipsing binaries~--~suggest that 13 of these
candidates have high probability of being planetary in nature.

@@

% \dfmtodo{More words here about comparison and interpretation.}

These long-period exoplanet candidates are potentially interesting candidates
for follow-up observations.
Using a probabilistic mass--radius relationship, we predict the masses of our
candidates and report predictions for the radial velocity amplitudes.
Unfortunately, since the target stars are faint and the amplitudes are small,
these targets are unlikely to be accessible with even the current
state-of-the-art high-precision instruments.
We also discuss the potential for astrometric follow-up using the forthcoming
data from the \gaia\ Mission with similarly discouraging results.

@@

\acknowledgments
It is a pleasure to thank
Jeff Coughlin,
So Hattori,
Hans-Walter Rix,
Dun Wang,
and
Angie Wolfgang
for helpful contributions to the ideas and code presented here.
